Cryptographic Hash Functions

### 2019-03-30 math408/presentation/hashPaper.tex
Did stuff

This paper will discuss cryptographic hash functions and many of the intriguing aspects of their nature. There will be two famous and widely-used hash functions that will be analyzed in detail, namely MD5 and SHA-256.

@@

\section{Hashing vs Encryption}

>>>>

This paper will discuss cryptographic hash functions and many of the intriguing aspects of their nature. Two famous and widely-used hash functions will be analyzed in detail, namely MD5 and SHA-256.

@@

\section{Hashing vs Encryption}
\tab Another word on collisions. Any well-developed hashing algorithm should have high collision resistance, but it is important to note that it is theoretically impossible to make a hash function that is completely collision-free. This is due to the fact that a hash function returns a fixed-length string. So, for a 128-bit hash, the output is always 32 characters. Possible characters for include the 26 letters and 0-9, so a total of 32 possible characters. This gives $26^{32}$ possible hashes, which is $1.9 x 10^{45}$. This is an astronomically high number, so breaking a hash of this size with brute force is infeasible, but given that there is a near-infinite number of inputs, there will always be possible collisions.
